Applied Intuition’s focus on delivering a robust Vehicle OS and ML-first autonomy stack resonates with how I like to work: build reliable capabilities end-to-end, measure what matters, and iterate quickly with customers. I’m drawn to your blend of rigorous engineering and fast, in-office collaboration, and I’m motivated by the chance to help translate real-world constraints into safe, measurable improvements in perception, prediction, and planning.

In recent roles, I owned the full ML lifecycle—from data to deployment. At MIR, I co-developed a multi-stage geospatial perception workflow for automated bike-path detection (Springer 2023), covering dataset curation, training, quantitative evaluation, and iterative improvement; the mapping, segmentation, and evaluation challenges mirror AV perception needs. At KISS, I built an experimental RAG system and an evaluation harness for prompt-engineered workflows, emphasizing input pipelines, latency/quality metrics, and reproducibility. Across projects I’ve implemented experiment tracking, offline/online evaluation, and packaging for reproducible deployment—practices I’d apply to system-in-the-loop model evaluation. I’m fluent in Python and steadily deepening my intermediate C++ to contribute to performance-critical components. My double M.Sc. (Business Application Architecture & Software Technology) complements hands-on work in ML, RL, and agentic systems.

I’m eager to build on Applied Intuition’s toolchain to extend ML capabilities and deliver trustworthy autonomy. Based in Germany, I can work primarily on-site in Stuttgart and would welcome sharing a concise 30/60/90-day ramp plan tailored to your AV model development workflows.