BCG Platinion’s focus on pairing strategic IT implementation with modern architectures, AI, and agile delivery resonates with how I work: translate business goals into secure, maintainable solutions that scale. I’m motivated by engagements where cloud, ML, microservices, and containerization are levers for measurable impact, and where client context and governance matter as much as technical elegance.

Recently, I built an experimental retrieval-augmented generation database and authored practical prompt-engineering materials that helped teams adopt LLM capabilities responsibly, with clear evaluation criteria, guardrails, and governance—foundations for cyber-resilient, production-ready AI. My master’s thesis extends this with an LLM-agent system for interactive data analysis, optimizing RAG patterns, tool orchestration, and cost-latency trade-offs. I also co-authored a Springer paper on a multi-stage geospatial ML pipeline, emphasizing reproducible workflows and model validation. Beyond AI, I have designed microservice-based solutions, Dockerized services, and CI/CD pipelines, applying DevOps, CD4ML, and CRISP-ML(Q) to improve reliability and maintainability. Internships at KPMG (digital finance) and Deutsche Bahn (AI infrastructure) strengthened my ability to deliver in large, regulated environments, and I led NLP-driven features for an e-democracy tool, aligning user journeys with responsible-AI practices.

I would bring this blend of rigor and pragmatism to designing and optimizing client architectures and customer journeys at BCG Platinion. I work well in interdisciplinary, client-facing teams, am fluent in German and English, and am flexible to travel. I’m open to the Consultant role or an Associate-level entry, depending on fit.