Eurazeo’s long-term, value-creation model—combining entrepreneurial investing with rigorous ESG and DEI commitments—resonates with how I work. I see clear opportunities to compound that edge with practical data and AI: from thematically driven sourcing and faster, more reproducible diligence, to scalable portfolio value-creation and transparent LP engagement. The firm’s collaborative culture and knowledge-sharing ethos are exactly the conditions where AI products deliver sustained impact.

I bring a double M.Sc. in Business Application Architecture & Software Technology and a B.Sc. in Business Informatics, with hands-on experience building an experimental RAG database and an LLM-agent system for interactive analysis. My research includes a Springer-published ML pipeline for geospatial detection and a CEUR paper (VotingAid, 2025) on applied LLM workflows. At KPMG (digital finance) and Deutsche Bahn (AI infrastructure), I worked cross-functionally on data readiness, governance, and deployment. Concretely, I can support Buyout/Growth/Venture teams with NLP-driven sourcing, IC-ready synthesis of CIMs and expert calls, and reproducible analytics for unit economics; IR with RAG copilots over DDQs and reporting; and Corporate Digital/Data with auditable pipelines and ESG/DEI metrics aligned to O+.

In the first 90 days, I would aim to launch a secure RAG copilot for IC memos and DDQ responses, build a sourcing heatmap with embeddings and watchlists, and pilot one portfolio AI use case with clear A/B metrics and ROI tracking—documented through open show-and-tells to enable reuse across teams.