Helsing’s mission to protect democratic societies through robust, real-time autonomy resonates with me. Designing and deploying reinforcement-learning agents that must generalize across platforms, operate under uncertainty, and withstand adversarial conditions is the kind of problem I enjoy: iterate carefully, validate thoroughly, and deliver explainable, trustworthy systems.

I am completing a double M.Sc. focused on RL, multi‑agent systems, and ML pipelines. My thesis builds an LLM‑agent system with tool use, planning loops, and a reproducible evaluation harness—experience applicable to agent design, training and evaluation loops, and end‑to‑end integration. At KISS I created an experimental RAG pipeline and embedded testing, CI/CD, and monitoring; at MIR I tackled geospatial computer vision with noisy, heterogeneous data and cross‑environment generalisation (Springer, 2023). I co‑authored VotingAid (CEUR, 2025). I re‑implement and extend RL papers, am comfortable with policy‑gradient and value‑based baselines, and write clean, tested Python with containerised experiments. Internships at Deutsche Bahn and KPMG with cross‑functional teams sharpened my communication and delivery.

At Helsing I would strengthen the multi‑agent RL stack by implementing state‑of‑the‑art methods, hardening evaluation and QA, and collaborating across teams to deploy models with clear telemetry and understood failure modes. I value responsible autonomy and open debate, and I’m eager to deepen large‑scale training while contributing from Munich or Berlin.