Qualifyze’s stakeholder-centric, outcome-driven culture resonates with how I like to build software: focus on real users, measure impact, and iterate with feedback. I’m completing a double M.Sc. in Business Application Architecture and Software Technology and have specialized in LLM agents, Retrieval-Augmented Generation, and MLOps—tools well-suited to regulated, data‑intensive contexts where traceability, robustness, and clear communication matter.

As a research associate, I built an experimental RAG database and authored prompt‑engineering materials; my thesis delivers an LLM‑agent system for interactive data analysis with evaluation, guardrails, and auditability. Earlier, I published on geospatial ML (Springer 2023) and co‑authored VotingAid (CEUR 2025), and I’ve shipped end‑to‑end services (RESTful frontend–backend, Docker) in team settings. I can add value by applying NLP to compliance/audit workflows—document ingestion and normalization, entity/relationship extraction (e.g., CAPAs, deviations, suppliers), and RAG to accelerate review—backed by reproducible pipelines, evaluation harnesses, and observability following CRISP‑ML(Q) principles. I also enjoy building metrics and internal tools that improve transparency and collaboration.

I thrive on feedback, take ownership, and communicate fluently in English and German. I’m a continuous learner, comfortable in international teams, and open to hybrid work in Barcelona or other hubs. I’d welcome a conversation to explore where these strengths align with your roadmap.