Traversals’ mission to make open-source data actionable in real time resonates with my focus on trustworthy, multilingual AI systems. I’m particularly drawn to your Data Fusion Platform and products like Company Risk Monitoring and Hybrid Threat Radar, where robust RAG, cross-lingual NLP, and geospatial analytics directly translate into better situational awareness. I enjoy the intersection of research and production: designing pipelines that are not only accurate and explainable, but also observable, reproducible, and easy for analysts to use.

In my double Master’s (Business Application Architecture & Software Technology) I specialized in LLM agents, RAG, and MLOps, publishing VotingAid (CEUR 2025) and geospatial ML work (Springer 2023). As a Research Associate, I built experimental RAG and agent workflows, taught prompt engineering, and worked on event detection and spatial aggregation. Practically, I implement cross-lingual retrieval (DE/EN/FR), entity linking/deduplication, and containerized services with CI/CD and CRISP-ML(Q)-aligned evaluation (e.g., nDCG, faithfulness, drift checks). Internships at KPMG and Deutsche Bahn strengthened my sense for enterprise reliability and secure data handling.

As a concrete next step, I propose a two-week “Guarded RAG” spike for Company Risk Monitoring: schema design, cross-lingual retrieval with citation grounding, answer-consistency checks, an evaluation harness and dashboard. The aim is measurable gains in retrieval and response quality, clear operational metrics, and a template to scale across your portfolio. I’m based in Germany and work fluently in German and English.